Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-26 analysis/study2.qmd
updated script with changes made in study1

data <- rbind(
  data,
  pool_coef(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)",unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
  pool_coef(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  pool_coef(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
  pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
)
```

@@

# data <- rbind(
#   data,
#   make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"),
#   make_rez(with = "PI_Changing", component="World Beliefs", name = "Changing"),
#   make_rez(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
#   make_rez(with = "PI_Good", component="World Beliefs", name = "Good"),
#   make_rez(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
#   make_rez(with = "PI_Safe", component="World Beliefs", name = "Safe"),
#   make_rez(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
#   make_rez(with = "PI_Alive", component="World Beliefs", name= "Alive"),
#   make_rez(with = "PI_Changing", component="World Beliefs", name = "Changing"),
#   make_rez(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
#   make_rez(with = "PI_Good", component="World Beliefs", name = "Good"),
#   make_rez(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
#   make_rez(with = "PI_Safe", component="World Beliefs", name = "Safe"),
#   make_rez(with = "PI_Understandable", component="World Beliefs", name = "Understandable")
# )
```

>>>>

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)",unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-4)"),
  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
)
```

@@

# data <- rbind(
#   data,
#   pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"),
#   pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing"),
#   pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
#   pool_coef(with = "PI_Good", component="World Beliefs", name = "Good"),
#   pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
#   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe"),
#   pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
# )
```
